### 2020-07-22 paper/main.tex
Introduction first draft wip

\usepackage{appendix}

@@

\section{Perfect Graphs}
Definition of perfect graphs.\\

Why are they interesting (Some examples of subclasses, and problems that are solvable for perfect graphs, including recognition and coloring).\\

Weak perfect graph theorem.\\

Berge graphs.

\subsection{Strong Perfect Graph Theorem}
Cite the paper, brief description of the theorem.

@@

>>>>

\usepackage{appendix}
\usepackage{todonotes}

\usepackage[
	style=alphabetic
]{biblatex}
\addbibresource{bbl.bib}

\newcommand{\TODO}{\todo[inline]}
\newcommand\Lovasz{Lovász }

% Language and typesetting notes:
%
% - Color, not Colour (American English)
% - Node not a Vertex of a graph

@@

\section{Perfect Graphs}
All graphs in this paper are finite, undirected and have no loops or parallel edges. We denote the chromatic number of graph $G$ by $\chi(G)$ and the cardinality of the largest clique of $G$ by $\omega(G)$. \emph{Coloring} of a graph means assigning every node of a graph a color. A coloring is \emph{valid} iff every two nodes sharing an edge have different colors. An \emph{optimal} coloring (if exists) is a valid coloring using only $\omega(G)$ colors.

Given a graph $G = (V,E)$ and a set $X \subseteq V$ by $G[X]$ we will denote a graph induced on $X$. A graph $G = (V,E)$ is \emph{perfect} iff for all $X \subseteq V$ we have $\chi(G[X]) = \omega(G[X])$.

\TODO{Give some examples why are these interesting, some subclasses, and problems that are solvable for perfect graphs, including recognition and coloring}

Given a graph $G$, its \emph{complement} $\overline{G}$ is a graph with the same vertex set and in which two distinct nodes $u, v$ are connected in $\overline{G}$ iff they are not connected in $G$. For example a clique in a graph becomes an independent set in its complement. A perfect graph theorem, first conjured by Berge in 1961 \cite{CB61} and then proven by \Lovasz in 1972 \cite{LL72} states that a graph is perfect iff its complement graph is also perfect. \todo{Should we give some proof of that here?}

\subsection{Strong Perfect Graph Theorem}
A \emph{hole} is an induced chordless cycle of length at least 4. An \emph{antihole} is an induced subgraph whose complement is a hole. A \emph{Berge} graph is a graph with no holes or antiholes of odd length.

In 1961 Berge conjured that a graph is perfect iff it is Berge in what has become known as a strong perfect graph conjecture. In 2001 Chudnovsky et al. have proven it and published the proof in an over 150 pages long paper \citetitle{MC06} \cite{MC06}.

@@

% \bibliographystyle{alpha}
\printbibliography
